Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-05-01 tex/ms.tex
expand gp length priors

HOGG: A model is a parameterized likelihood function, with prior PDFs on the nuisance parameters (at least)...

HOGG: There is a likelihood for the photometry and for the spectroscopy...

HOGG: Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...

@@

We estimate the posterior through MCMC sampling after an initial round
of optimization using Powell's method.  The specific sampling
algorithm we use is the affine-invariant ensemble sampling scheme of
\citet{goodman}, as implemented in the \texttt{emcee} package \citep{emcee}
Unlike typical Metropolis-Hastings MCMC sampling, the affine-invariant
sampler does not require the specification of step sizes in each
dimension.  {\color{blue}ASSESSING SAMPLER CONVERGENCE}

At each iteration of the sampler the photometric and spectroscopic
likelihood are computed, multiplied together, and multiplied by the
the prior probability of that parameter position to obtain an estimate
of the posterior probability for those parameters given the data.

@@

{\color{blue} BDJ - This paragraph is probably too calibration
focused. We want to focus more on spec + phot combinations.  At least,
this paragraph should not be in the discussion section.}
Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using that observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
spectrophotometric calibration, the full distribution of the possible
calibrations should be inferred from our probabilistic knowledge of
the calibration object and forward propogated
\citep[e.g.][]{lee11}. Indeed, even if the calibration object is known
perfectly, the observation of it will be noisy and thus so will the
inferred calibration. Once this forward propogation of calibration
uncertainty is done, the only distinction between 'calibration'
objects and targets of interest is the uncertainty in the model for
the object and the level of uncertainty in the observed object
spectrum -- this is why calibration objects are typically bright and
simple.  If one is interested in inferring parameters of interest of
spectral models of astrophysical objects, then there is often no
reason not to use those objects themselves as calibration objects
(especially if you expect your calibration to be spatially or
temporally variable, or to change with the brightness of the object)

>>>>

HOGG: A model is a parameterized likelihood function, with prior PDFs on the nuisance parameters (at least)...
There is a likelihood for the photometry and for the spectroscopy...
Each of these penalizes the difference between a column vector of data and a column vector of model expectation value...

@@

We estimate the posterior through MCMC sampling after an initial round
of optimization using Powell's method.  The specific sampling
algorithm we use is the affine-invariant ensemble sampling scheme of
\citet{goodman}, as implemented in the \texttt{emcee} package
\citep{emcee} Unlike typical Metropolis-Hastings MCMC sampling, the
affine-invariant sampler does not require the specification of step
sizes in each dimension.

At each iteration of the sampler the photometric and spectroscopic
likelihood are computed, multiplied together, and multiplied by the
the prior probability of that parameter position to obtain an estimate
of the posterior probability for those parameters given the
data. {\color{blue}Assessing sampler convergence.}

@@

{\color{blue} BDJ - This paragraph is probably too calibration
focused. We want to focus more on spec + phot combinations.  At least,
this paragraph should not be in the discussion section.}
Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using that observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
spectrophotometric calibration, the full distribution of the possible
calibrations should be inferred from our probabilistic knowledge of
the calibration object and forward propogated
\citep[e.g.][]{lee11}. Indeed, even if the calibration object is known
perfectly, the observation of it will be noisy and thus so will the
inferred calibration. Once this forward propogation of calibration
uncertainty is done, the only distinction between 'calibration'
objects and targets of interest is the uncertainty in the model for
the object and the level of uncertainty in the observed object
spectrum -- this is why calibration objects are typically bright and
simple.  If one is interested in inferring parameters of interest of
spectral models of astrophysical objects, then there is often no
reason not to use those objects themselves as calibration objects,
especially if you expect your calibration to be spatially or 
temporally variable, or to change with the brightness of the object.
